---
title: "Pitch for Shiny App"
author: "srishtiS"
date: "06/11/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction 
I have used the dataset mtcars.csv from the dataset library of Rstudio. 
if you don't have it then install using 

```{r echo = TRUE, message=FALSE, warning=FALSE}
install.packages("datasets")
```


and then add the required library before using the dataset 

```{r echo = TRUE}
library(datasets)
data("mtcars")
```

## Check out the headers and the values

```{r echo = TRUE}
head(mtcars)
```



## Do Exploratory Analysis

```{r cars, echo = TRUE}
summary(mtcars)
```

mpg is Miles per Gallon and the other 10 variables affect the MPG 

## Usage of the App 

The App gives you a boxplot for mpg vs the 10 variables. For eg below is the plot for Mode vs MPG and you can notice that the Manual Mode is much economical. 

``` {r echo = FALSE, message = FALSE, warning = FALSE}
boxplot(mpg ~ am, data = mtcars,
        col = c("blue", "yellow"),
        ylab = "Miles per Gallon (mpg)",
        main = "MPG by Transmission Type")
```


